Approximate Network Matching

### 2024-02-19 paper.qmd
Update paper.qmd
Co-authored-by: Robin Lovelace <Robinlovelace@users.noreply.github.com>

- use the approximate network matching to create a list of _very strong_ candidate matches with a known shared overlap amount. 
- The result of the approximate network match can be taken and utilized for vertical conflation using many different approaches 
- in this paper we introduce a method of spatial interpolation of linear features

>>>>

- use the approximate network matching to create a list of _strong_ candidate matches with a known shared overlap amount. 
- The result of the approximate network match can be taken and utilized for 'vertical conflation' using many different approaches 
- in this paper we introduce a method of spatial interpolation of linear features
